Analyze Stop Data

### 2016-07-29 AnalysizeStop.Rmd
graph updates

stop_race <- ggplot(stop_by, aes(x = Race, fill = Gender)) + geom_bar()
stop_age <- ggplot(stop_by, aes(x = AgeRange, fill = Gender)) + geom_bar()
stop_reason <- ggplot(stop_by, aes(x = Reason, fill = Gender)) + geom_bar()
stop_time <- ggplot(stop_by, aes(x = hour, fill = AgeRange)) + geom_bar()

>>>>

#Sample graph
stop_race <- ggplot(stop_by, aes(x = Race, fill = Gender)) + 
  geom_bar(aes(y = ..count../sum(..count..))) + 
  labs(y = "Density") +
  facet_wrap(~Reason)

stop_age <- ggplot(stop_by, aes(x = AgeRange, fill = Gender)) + geom_bar() 
stop_reason <- ggplot(stop_by, aes(x = Reason, fill = Gender)) + geom_bar()
stop_time <- ggplot(stop_by, aes(x = hour, fill = AgeRange)) + geom_bar()

stop_race
